Carbonate chemistry at Ny-Ålesund

### 2021-12-29 awipev-CO2.Rmd
fixed TeX issue

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
reg <- ggreg(
  xdata = d_all$sal_fb_mix,
  ydata = d_all$at,
  type = "OLS",
  plot = TRUE,
  title = "Discrete total alkalinity vs salinity",
  #subtitle = "",
  xlab = "Salinity",
  ylab = TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")

# Same plot for paper
p_at_s <- d_all_at_discrete %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"))  +
  stat_smooth(method = "lm", col = "blue", size = 0.5) +
  Mytheme(size_labs = 9)
ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
reg <- ggreg(
  xdata = d_all$pco2_fb_insi_temp,
  ydata = d_all$pco2_calc_fb_insi_temp,
  type = "MA",
  plot = TRUE,
  title = "pCO2 normalized at in situ temperature",
  #subtitle = "",
  xlab = latex2exp::TeX("Measured $pCO_{2}(\\mu atm)$"),
  ylab = latex2exp::TeX("Calculated $pCO_{2}(\\mu atm)$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/pco2_calc_meas.png", plot = reg$plot)
```

>>>>

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
reg <- ggreg(
  xdata = d_all$sal_fb_mix,
  ydata = d_all$at,
  type = "OLS",
  plot = TRUE,
  title = "Discrete total alkalinity vs salinity",
  #subtitle = "",
  xlab = "Salinity",
  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")

# Same plot for paper
p_at_s <- d_all_at_discrete %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  stat_smooth(method = "lm", col = "blue", size = 0.5) +
  Mytheme(size_labs = 9)
ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
reg <- ggreg(
  xdata = d_all$pco2_fb_insi_temp,
  ydata = d_all$pco2_calc_fb_insi_temp,
  type = "MA",
  plot = TRUE,
  title = "pCO2 normalized at in situ temperature",
  #subtitle = "",
  xlab = latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
  ylab = latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/pco2_calc_meas.png", plot = reg$plot)
```
